Visegrad Countries and Education Challenges : An

### 2024-03-15 writing/paper.Rmd
final version complete finally

---
title: "Untitled"
author: "Bennour Mohamed Hsin"
date: "2024-02-04"
output:
  pdf_document: default
  html_document: default
---

@@

data_full <- readr::read_csv('clean_data/clean_united_data.csv')
dea_out_1 <- read_rds(here::here("results", "dea_out_1.rds"))
```

@@

Education is the backbone of long-term economic prosperity. Thus, studying the educational landscapes of different countries for comparative reasons allows researchers to derive best practices that can be moulded into policies for the benefit of the collective well-being of communities in the regions. In this context, we conduct a detailed examination of school efficiency across 1190 schools at the NUTS2 regions of the Visegrad countries, namely Hungary, Poland, the Czech Republic, and the Slovak Republic, utilizing the rich dataset provided by PISA 2019. The dataset compiled for this research consists of an integrated mix of data, where student-level performance metrics and scores are aggregated to reflect school-level outcomes. This comprehensive dataset includes detailed information about the internal environment of each school, as well as the external factors surrounding it. Our analysis is threefold: first, we employ Data Envelopment Analysis (DEA) that identifies key factors contributing to school effectiveness and best practices in terms of student performancces; second, we employ a double-bootstrap procedure to estimate the contribution of various non-discretionary variables on school efficiency (related to the schools and to the region in question); and third, we conduct a Meta-Efficiency analysis across the four countries to unravel hidden patterns of inefficiencies. Our approach provides comprehensive analysis and insights that have actual practical policy implications, which can be tailored to the regional context of each of the countries in our study.

@@

For this paper we decided to adopt this approach where we estimate (non-parametrically) the production function of our school sample with the means of Data-envelopment-analysis (or DEA, yielding efficiency scores) in the first stage then we use a a double-bootstrap process (following [@sw2007]) to estimate a truncated regression that enables inference on some non-discretionary factors within the DMUs and around it. 

@@

```{r echo=FALSE}
data_full %>% 
  na.omit() %>% 
  group_by(CNT) %>% 
  summarise(count = n()) %>% 
  gt()
```
Table 2 provide a full description of the final

```{r echo=FALSE}

variables <- c("SC001Q01TA", "SC011Q01TA", "SCHSIZE", "SC002Q01TA", "SC002Q02TA",
               "STRATIO", "TOTAT", "student_behavior_issue_mean", "teacher_behavior_issue_mean",
               "resources_issue_mean", "staff_issues_mean", "total_homework_time",
               "total_class_periods", "mean_PV_science", "mean_PV_reading", "mean_PV_math",
               "mean_reading_attitude", "mean_science_attitude", "mean_math_attitude")

data_full %>% 
  na.omit() %>% 
  # group_by(CNT) %>% 
  summarise(
    across(
      all_of(variables),
      list(min = ~min(.x, na.rm = TRUE), 
                         max = ~max(.x, na.rm = TRUE),
                         mean = ~mean(.x, na.rm = TRUE), 
                         sd = ~sd(.x, na.rm = TRUE)), 
      .names = "{.col}__{.fn}"
    )
  ) %>% 
  pivot_longer(1:76, names_to = 'variable', values_to = 'value') %>% 
  separate(variable, c('variable', 'measure'), sep = '__') %>% 
  pivot_wider(names_from = measure, values_from = value) %>% 
  gt()
```
<div align="center">

```{r echo=FALSE}

data_full %>% 
  na.omit() %>% 
  group_by(CNT) %>%
  summarise(
    across(
      all_of(variables),
      list(min = ~min(.x, na.rm = TRUE), 
                         max = ~max(.x, na.rm = TRUE),
                         mean = ~mean(.x, na.rm = TRUE), 
                         sd = ~sd(.x, na.rm = TRUE)), 
      .names = "{.col}__{.fn}"
    )
  ) %>% 
  pivot_longer(2:77, names_to = 'variable', values_to = 'value') %>% 
  separate(variable, c('variable', 'measure'), sep = '__') %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  gt() %>% 
  tab_options(
    table.width = pct(50) # Ensure the table uses the full page width
    # column_labels.text_wrap = TRUE, # Wrap column headers
    # data_row.text_wrap = TRUE # Wrap data rows
  )
```
</div>

@@

Choosing the inputs that will be used in our analysis is very important for few reasons. First, in the context of analyzing schools' efficiency, the inputs of schools are almost fixed, thus we have to use plausible inputs with enough variation. We decided to use as  inputs the students to teacher ratio (STRATIO) which has been used in other studies such as [@Bessent_Bessent_1980; @Charnes_et_al_1981;  @Ray_1991; @Johnes_1996; @Cooper_Cohn_1997; @Heshmati_Kumbhakar_1997;  @Afonso_Aubyn_2006; @Johnes_Yu_2008; @Cherchye_et_al_2010; @Agasisti_2011b; @Agasisti_2013; @Johnes_2013; @Zoghbi_et_al_2013] among others and the total number of schooling hours (total_class_period)  which has been used in similar studies such as [@rebai2020; @benyahia2018] to cite a few.

```{r echo=FALSE}
data_full %>% 
  na.omit() %>% 
  select(CNT, STRATIO, total_class_periods) %>% 
  group_by(CNT) %>%
  summarise(
    across(
      c(STRATIO, total_class_periods),
      list(min = ~min(.x, na.rm = TRUE), 
                         max = ~max(.x, na.rm = TRUE),
                         mean = ~mean(.x, na.rm = TRUE), 
                         sd = ~sd(.x, na.rm = TRUE)), 
      .names = "{.col}__{.fn}"
    )
  ) %>% 
  pivot_longer(2:ncol(.), names_to = 'variable', values_to = 'value') %>% 
  separate(variable, c('variable', 'measure'), sep = '__') %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  gt()
```

@@

For the output we will adopt variables depicting aggregate (average) students' test scores by school, these aggregations describe the average scores students got for each school in MATH, READING, and SCIENCE. This is in accordance with multiple studies in this context such as[@Bessent_Bessent_1980; @Charnes_et_al_1981; @Afonso_Aubyn_2006;  @Cherchye_et_al_2010; @Essid_et_al_2010; @Essid_et_al_2013; @De_Witte_Kortelainen_2013; @De_Witte_et_al_2013; @rebai2020; @benyahia2018]

```{r echo=FALSE}
data_full %>% 
  na.omit() %>% 
  select(CNT, mean_PV_science, mean_PV_reading, mean_PV_math) %>% 
  group_by(CNT) %>%
  summarise(
    across(
      c(mean_PV_science, mean_PV_reading, mean_PV_math),
      list(min = ~min(.x, na.rm = TRUE), 
                         max = ~max(.x, na.rm = TRUE),
                         mean = ~mean(.x, na.rm = TRUE), 
                         sd = ~sd(.x, na.rm = TRUE)), 
      .names = "{.col}__{.fn}"
    )
  ) %>% 
  pivot_longer(2:ncol(.), names_to = 'variable', values_to = 'value') %>% 
  separate(variable, c('variable', 'measure'), sep = '__') %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  gt()
```

#### Non-discretionary variables

The final piece of our data is the non-discretionary variables which we will use to assess the contribution of environmental variables in the schools and around them on the their efficiency. These variables are typically used in a two-stage analysis such as ours and provide insights that enables inference in order to understand what can be done (according to the sample of the study) to imptove the school efficiency that maximizes the output of test scores. We incorporated in the second stage of our analysis variables regarding behavior issues (absence, delinquency, harassment, violence, etc) of students (student_behavior_issue_mean), teachers (teacher_behavior_issue_mean), and staff  (staff_issues_mean), as well as issues of available resources in the premis including personal and material resources  (resources_issue_mean), number of schools in the area (SC011Q01TA, 3 none, 2 one school, 1 two ore more schools),  Community type where the school is located (SC001Q01TA, 1 urban, 0 rural), school size depicted by the number of enrolled students in the school (SCHSIZE), and the total number of all teachers at the school (TOTAT).

```{r echo=FALSE}
data_full %>% 
  na.omit() %>% 
  select(CNT, 
         student_behavior_issue_mean,
          teacher_behavior_issue_mean,
          resources_issue_mean,
          staff_issues_mean,
          # total_homework_time, #I dont think this is necessary
          # total_class_periods,
          SC011Q01TA, # number of schools in the area (3 none, 2 one school, 1 two ore more schools)
          # STRATIO,
          SCHSIZE,
          SC001Q01TA, # Community type where the school is located
          TOTAT # Total number of all teachers at the school
         ) %>% 
  group_by(CNT) %>%
  summarise(
    across(
      c(student_behavior_issue_mean,
          teacher_behavior_issue_mean,
          resources_issue_mean,
          staff_issues_mean,
          # total_homework_time, #I dont think this is necessary
          # total_class_periods,
          SC011Q01TA, # number of schools in the area (3 none, 2 one school, 1 two ore more schools)
          # STRATIO,
          SCHSIZE,
          SC001Q01TA, # Community type where the school is located
          TOTAT # Total number of all teachers at the school
        ),
      list(min = ~min(.x, na.rm = TRUE), 
                         max = ~max(.x, na.rm = TRUE),
                         mean = ~mean(.x, na.rm = TRUE), 
                         sd = ~sd(.x, na.rm = TRUE)), 
      .names = "{.col}__{.fn}"
    )
  ) %>% 
  pivot_longer(2:ncol(.), names_to = 'variable', values_to = 'value') %>% 
  separate(variable, c('variable', 'measure'), sep = '__') %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  gt()
```

@@

However, an interesting debate has took place regarding the statistical plausibility of second stage regression. On the one hand, advocates of this approach argue that the simplicity and versatility of the approach allows for valuable and practical insight. OLS or Tobit regressions are usually used in this context allowing for inference, in fact [@hoff2007] provided a review of the use of tobit and OLS regression in a second stage, and advocated for the use of tobit. On the other hand opponents to the approach advocate for a more careful specifications, since a two-stage analysis doesn't stem for a data generating process (DGP), thus it's quite difficult to understand what is exactly being estimated in the second stage. One of the earliest critics of this approach was [@grosskopf1996] who specified that other than the lack of a DGP, there's a possibility that these non-discretionary variables of the second stage can be correlated with the output efficiency of the first stage. Both [@grosskopf1996] and [@ramalho2010] argued against the use of linear models in the second stage. Building on this criticism, [@simar2007] was the first paper that coherently justified the use of a two-stage DEA proposing a DGP and two bootstrap algorithm that enable inference in the second stage with a truncated regression. The basic idea behind [@simar2007] work, is that DEA efficiency scores are non-parametrically estimated, thus they are a non-observed estimate of an unkown efficiency frontier which means that these scores do not account for stochasticity (i.e: any deviation from the efficiency frontier is entirely due to inefficiency) which means that using non-parametric methods in the second stage is more appropriate, hence the bootstrap algorithms.

@@

```{r echo=FALSE}
summary_stats <- dea_out_1 %>%
  mutate(efficiency_scores = map(dea_out, ~.$eff)) %>%
  summarise(
    mean_efficiency = mean(unlist(efficiency_scores)),
    sd_efficiency = sd(unlist(efficiency_scores)),
    min_efficiency = min(unlist(efficiency_scores)),
    max_efficiency = max(unlist(efficiency_scores))
  )
summary_stats %>% 
  gt()
```

```{r echo=FALSE}
# Analysis 2: Plot distribution of efficiency scores for each country.
dea_out_1 %>%
  mutate(efficiency_scores = map(dea_out, ~.$eff)) %>%
  unnest(efficiency_scores) %>%
  ggplot(aes(x = efficiency_scores)) +
  geom_histogram(bins = 30, fill = "skyblue", color = "skyblue") +
  facet_wrap(~CNT) +
  labs(title = "Distribution of Efficiency Scores by Country",
       subtitle = "Including Fully efficient schools",
       x = "Efficiency Score",
       y = "Frequency")
```

```{r echo=FALSE}
# Extract efficiency scores, compute quartiles, and mark fully efficient schools.
dea_by_quartile <- dea_out_1 %>% 
  mutate(
    eff_scores =  map(dea_out, ~pluck(.x, "eff"))
  ) %>% 
  unnest(eff_scores) %>% 
  mutate(
    full_eff = if_else(eff_scores == 1, 1, 0),
    quartiles = cut(eff_scores,
                    breaks = quantile(eff_scores, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = TRUE),
                    labels = c('Q1', 'Q2', 'Q3', 'Q4'),
                    include.lowest = TRUE)
  )

# Plot histogram of efficiency scores by country and quartile for non-fully efficient schools.
dea_by_quartile %>% 
  filter(full_eff != 1) %>% 
  ggplot(aes(x = eff_scores)) +
  geom_histogram(bins = 30, fill = "skyblue", color = "skyblue") +
  facet_grid(quartiles ~ CNT) +
  labs(title = "Distribution of Efficiency Scores by Country and Quartile\nFor non Efficient Schools",
       x = "Efficiency Score",
       y = "Frequency")
```

```{r echo=FALSE}
# Plot boxplot of efficiency scores by country and quartile for non-fully efficient schools.
dea_by_quartile %>% 
  filter(full_eff != 1) %>% 
  ggplot(aes(x = quartiles, y = eff_scores)) +
  geom_boxplot() +
  facet_grid(~ CNT) +
  labs(title = "Distribution of Efficiency Scores by Country and Quartile\nFor non Efficient Schools",
       x = "Quartile",
       y = "Efficiency Score")
```

```{r echo=FALSE, warning=FALSE}
# Calculate and display count and percentage of schools in each quartile, including fully efficient ones.
dea_by_quartile %>% 
  mutate(
    quartiles_ineff = if_else(full_eff == 1, "FE", quartiles)
  ) %>% 
  count(quartiles_ineff) %>% 
  mutate(
    p = case_when(
      CNT == 'CZE' ~ (n / 417)*100,
      CNT == 'HUN' ~ (n / 254)*100,
      CNT == 'POL' ~ (n / 238)*100,
      CNT == 'SVK' ~ (n / 271)*100
    ),
    p = glue::glue('({round(p, 2)}%)')
  ) %>% 
  unite(p, c('n','p'), sep = '  ') %>% 
  pivot_wider(names_from = quartiles_ineff, values_from = p) %>% 
  ungroup() %>% 
  gt()
```

```{r echo=FALSE}
# Create and plot a stacked bar chart showing the percentage distribution of schools by efficiency quartile and country.
dea_by_quartile %>% 
  mutate(
    quartiles_ineff = if_else(full_eff == 1, "FE", quartiles)
  ) %>% 
  count(quartiles_ineff) %>% 
  ggplot() +
  geom_col(
    aes(
      x = n, 
      y = CNT,
      .group = CNT,
      fill = quartiles_ineff
    ), position = "dodge"
  ) +
  labs(title = "Percentage of Fully Efficient (FE) and Quartile distribution\nof Inefficient Schools by Country",
       x = "Percentage",
       y = "Country")

```{r echo=FALSE}
# Function to calculate the number of zero and non-zero values in each column
count_zeros_and_nonzeros <- function(matrix) {
  # Count non-zero values
  non_zero_counts <- colSums(matrix != 0)
  # Count zero values
  zero_counts <- colSums(matrix == 0)
  # Combine into a data frame for easier viewing
  # Count non-zero values
  non_zero_avg <- colMeans(matrix != 0)
  # Count zero values
  zero_avg <- colMeans(matrix == 0)

>>>>

---
title: "Visegrad Countries and Education Challenges : An
Efficiency Analysis"
author: "Bennour Mohamed Hsin - University of Pécs - Faculty of Business and Economics"
date: "2024-02-04"
output:
  pdf_document: 
    latex_engine: xelatex
    includes:
      in_header: header.tex
bibliography: refs.bib
---

@@

theme_set(theme_light())

data_full <- readr::read_csv('clean_data/clean_united_data.csv')
dea_out_1 <- read_rds(here::here("results", "dea_out_1.rds"))
inputs <- c("CPERIODS", "STRATIO")
outputs <- c("SCIENCE", "READING", "MATH")
envs <- c("STUBI", "TEABI", "RESSI", "STAFI", "COMP", "SCSIZE", "LOC", "TOTAT")
```

\newpage

@@

Education is the backbone of long-term economic prosperity. Thus, studying the educational landscapes of different countries for comparative reasons allows researchers to derive best practices that can be moulded into policies for the benefit of the collective well-being of communities in the regions. In this context, we conduct a detailed examination of school efficiency across 1190 schools at the NUTS2 regions of the Visegrad countries, namely Hungary, Poland, the Czech Republic, and the Slovak Republic, utilizing the rich dataset provided by PISA 2019. The dataset compiled for this research consists of an integrated mix of data, where student-level performance metrics and scores are aggregated to reflect school-level outcomes. This comprehensive dataset includes detailed information about the internal environment of each school, as well as the external factors surrounding it. Our analysis is threefold: first, we employ Data Envelopment Analysis (DEA) that identifies key factors contributing to school effectiveness and best practices in terms of student performances; second, we employ a double-bootstrap procedure to estimate the contribution of various non-discretionary variables on school efficiency.

@@

For this paper we decided to adopt this approach where we estimate (non-parametrically) the production function of our school sample with the means of Data-envelopment-analysis (or DEA, yielding efficiency scores) in the first stage then we use a a double-bootstrap process (following [@simar2007]) to estimate a truncated regression that enables inference on some non-discretionary factors within the DMUs and around it. 

@@

```{r tab1, echo=FALSE}
data_full %>% 
  na.omit() %>% 
  group_by(CNT) %>% 
  summarise(count = n()) %>% 
  gt() %>% 
  tab_header(
    title = 'Table 1: Number of observation (schools) per country' 
  )
```

Table 2 provide a full description of the final data across all the visegrad countries.

```{r tab2, echo=FALSE}

data_full %>% 
  na.omit() %>% 
  # group_by(CNT) %>% 
  summarise(
    across(
      all_of(c(inputs, outputs, envs)),
      list(min = ~min(.x, na.rm = TRUE), 
                         max = ~max(.x, na.rm = TRUE),
                         mean = ~mean(.x, na.rm = TRUE), 
                         sd = ~sd(.x, na.rm = TRUE)), 
      .names = "{.col}__{.fn}"
    )
  ) %>% 
  pivot_longer(1:ncol(.), names_to = 'variable', values_to = 'value') %>% 
  separate(variable, c('variable', 'measure'), sep = '__') %>% 
  pivot_wider(names_from = measure, values_from = value) %>% 
  gt(rowname_col = 'variable') %>% 
  fmt_number(
    columns = 2:last_col(),
    decimals = 3
  ) %>%
  # Group Rows based on category (e.g., 'Input Variables', 'Output Variables', 'Environmental Variables')
  tab_row_group(
    label = "Input Variables",
    rows = variable %in% c("CPERIODS", "STRATIO")
  ) %>%
  tab_row_group(
    label = "Output Variables",
    rows = variable %in% c("SCIENCE", "READING", "MATH")
  ) %>%
  tab_row_group(
    label = "Environmental Variables",
    rows = variable %in% c("STUBI", "TEABI", "RESSI", "STAFI", "COMP", "SCSIZE", "LOC", "TOTAT")
  ) %>% 
  tab_header(
    title = 'Table 2: Descriptive statistics of all the variables for the entire sample' 
  )
```

\blandscape
\begin{table}
\centering

Table 3: Descriptive statistics of all the variables for each country
\newlength\holdLTleft\newlength\holdLTright\setlength\holdLTleft{\LTleft}\relax\setlength\holdLTright{\LTright}\relax\setlength\LTleft{0\linewidth}
\setlength\LTright{0\linewidth}\begin{longtable}{@{\extracolsep{\fill}}l|rrrrrrrrrrrrr}
\toprule
\multicolumn{1}{l}{} & \multicolumn{2}{c}{Input Variables} & \multicolumn{3}{c}{Output Variables} & \multicolumn{8}{c}{Environmental Variables} \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-6} \cmidrule(lr){7-14}
\multicolumn{1}{l}{} & CPERIODS & STRATIO & SCIENCE & READING & MATH & STUBI & TEABI & RESSI & STAFI & COMP & SCSIZE & LOC & TOTAT \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{14}{l}{CZE} \\ 
\midrule\addlinespace[2.5pt]
min & $4.000$ & $3.250$ & $237.794$ & $323.644$ & $349.407$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $13.000$ & $0.000$ & $4.000$ \\ 
max & $41.125$ & $100.000$ & $675.767$ & $664.219$ & $661.315$ & $3.600$ & $3.400$ & $4.000$ & $4.000$ & $3.000$ & $1,910.000$ & $1.000$ & $126.500$ \\ 
mean & $30.157$ & $13.042$ & $503.257$ & $493.412$ & $492.427$ & $1.895$ & $1.862$ & $1.886$ & $1.954$ & $1.617$ & $459.782$ & $0.569$ & $36.267$ \\ 
sd & $4.664$ & $5.567$ & $69.887$ & $68.933$ & $66.563$ & $0.474$ & $0.501$ & $0.675$ & $0.683$ & $0.860$ & $244.159$ & $0.496$ & $19.091$ \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{14}{l}{HUN} \\ 
\midrule\addlinespace[2.5pt]
min & $3.000$ & $1.000$ & $322.458$ & $241.531$ & $265.364$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $9.000$ & $0.000$ & $9.000$ \\ 
max & $53.000$ & $25.409$ & $659.594$ & $628.476$ & $636.929$ & $3.800$ & $4.000$ & $4.000$ & $3.750$ & $3.000$ & $1,461.000$ & $1.000$ & $123.000$ \\ 
mean & $29.720$ & $10.892$ & $472.745$ & $458.126$ & $456.751$ & $1.650$ & $1.644$ & $2.154$ & $1.941$ & $1.675$ & $497.228$ & $0.714$ & $45.182$ \\ 
sd & $7.139$ & $3.212$ & $76.142$ & $83.917$ & $77.683$ & $0.572$ & $0.501$ & $0.823$ & $0.604$ & $0.836$ & $272.114$ & $0.453$ & $21.831$ \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{14}{l}{POL} \\ 
\midrule\addlinespace[2.5pt]
min & $3.000$ & $1.000$ & $358.259$ & $235.286$ & $305.966$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $23.000$ & $0.000$ & $4.500$ \\ 
max & $42.840$ & $20.192$ & $638.343$ & $627.149$ & $632.535$ & $3.600$ & $3.400$ & $3.750$ & $4.000$ & $3.000$ & $1,428.000$ & $1.000$ & $124.500$ \\ 
mean & $30.769$ & $10.093$ & $500.726$ & $489.696$ & $489.461$ & $2.026$ & $1.685$ & $1.659$ & $1.708$ & $1.312$ & $508.714$ & $0.808$ & $48.912$ \\ 
sd & $7.057$ & $3.438$ & $63.010$ & $71.327$ & $62.903$ & $0.526$ & $0.531$ & $0.669$ & $0.630$ & $0.636$ & $297.766$ & $0.395$ & $23.701$ \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{14}{l}{SVK} \\ 
\midrule\addlinespace[2.5pt]
min & $3.000$ & $3.143$ & $294.747$ & $278.503$ & $282.693$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $1.000$ & $42.000$ & $0.000$ & $7.000$ \\ 
max & $44.111$ & $21.615$ & $645.012$ & $648.836$ & $642.726$ & $4.000$ & $3.200$ & $4.000$ & $3.750$ & $3.000$ & $1,344.000$ & $1.000$ & $102.500$ \\ 
mean & $27.001$ & $12.403$ & $466.918$ & $452.341$ & $468.762$ & $1.793$ & $1.704$ & $2.024$ & $1.827$ & $1.549$ & $389.675$ & $0.488$ & $31.006$ \\ 
sd & $5.642$ & $3.209$ & $63.869$ & $64.199$ & $64.536$ & $0.596$ & $0.491$ & $0.830$ & $0.653$ & $0.815$ & $224.078$ & $0.501$ & $16.131$ \\ 
\bottomrule
\end{longtable}
\setlength\LTleft{\holdLTleft}
\setlength\LTright{\holdLTright}

\end{table}
\elandscape
\newpage

@@

Choosing the inputs that will be used in our analysis is very important for few reasons. First, in the context of analyzing schools' efficiency, the inputs of schools are almost fixed, thus we have to use plausible inputs with enough variation. We decided to use as  inputs the students to teacher ratio (STRATIO) which has been used in other studies such as [@Bessent_Bessent_1980; @Charnes_et_al_1981;  @Ray_1991; @Johnes_1996; @Cooper_Cohn_1997; @Heshmati_Kumbhakar_1997;  @Afonso_Aubyn_2006; @Johnes_Yu_2008; @Cherchye_et_al_2010; @Agasisti_2011b; @Agasisti_2013;  @Zoghbi_et_al_2013] among others and the total number of class periods per week (CPERIODS)  which has been used in similar studies such as [@rebai2020; @benyahia2018] to cite a few. 
The data (per table 2) shoes that Czech Republic has an average of 30.157 class periods, similar to Poland's average of 30.769, although these are higher values compared to Hungary (29.720) and the Slovak Republic (27.001). Hungary exhibits the widest range with class periods extending up to 53, indicating significant variability in schooling intensity.

@@

For the output we will adopt variables depicting aggregate (average) students' test scores by school, these aggregations describe the average scores students got for each school in MATH, READING, and SCIENCE. This is in accordance with multiple studies in this context such as[@Bessent_Bessent_1980; @Charnes_et_al_1981; @Afonso_Aubyn_2006;  @Cherchye_et_al_2010; @Essid_et_al_2010; @Essid_et_al_2013; @De_Witte_Kortelainen_2013; @De_Witte_et_al_2013; @rebai2020; @benyahia2018]
The descriptives in table 2 show that Poland and the Czech Republic present closely matched average scores in science (500.726 and 503.257 respectively), but Czech Republic seems to have an advantage compared to the rest of the countries in reading, and math as well, indicating that academic achievements vary widely across countries according to the survey. The Slovak Republic, with an average science score of 466.918, and Hungary, with 472.745, show lower performance levels in comparison, whereas Hungary shows the largest variations in all scores among the four countries with a standard deviation amounting to 76.142 in science, 83.917 for reading, and 77.683 for math.

#### Environmental variables

The final piece of our data is the environmental (non-discretionary) variables which we will use to assess the contribution of environmental variables in the schools and around them on their efficiency. These variables are typically used in a two-stage analysis such as ours and provide insights that enable inference in order to understand what can be done (according to the sample of the study) to improve school efficiency that maximizes the output of test scores. We incorporated in the second stage of our analysis variables regarding behavior issues aggregated by means of other variables for students (STUBI, includes aspects such as truancy, disrespect towards teachers, substance abuse, and bullying), teachers (TEABI, reflecting the degree to which teachers meet individual students' needs, their absenteeism, resistance to change, strictness, and preparation for classes), and staff (STAFI, This variable measures the aspects related to the school's staff, encompassing the availability and quality of teaching staff and assisting personnel. It checks if there are enough teachers and assistants, and whether they are qualified and capable to meet educational demands.), as well as issues of available resources in the premises including personal and material resources (RESSI, this variable reflects the school's environment and resources, focusing on the availability of educational materials like textbooks and IT equipment, as well as the school's physical facilities such as buildings and heating/cooling systems. Essentially, it looks at whether students have the materials they need and a conducive learning environment). Both the STAFI and RESSI varaibles are observed in [@benyahia2018]. Also we use the number of schools in the area (COMP, 3 none, 2 one school, 1 two or more schools) observed in studies like [@Agasisti2013; @BradleyEtAl2001; @rebai2020], Community type where the school is located (LOC, 1 urban, 0 rural) observed in studies such as [@BurneyEtAl2013; @MizalaEtAl2002;  @rebai2020], school size depicted by the number of enrolled students in the school (SCSIZE), and the total number of all teachers at the school (TOTAT).
In our data, Poland exhibits the highest mean in student behavioral issues (2.026), which may impact the teaching environment. However, its mean for teacher behavioral issues is relatively low (1.685), indicating that despite student behavior, teacher performance remains less affected. However Slovakia presents the highest maximum of student behavioral issues (4.0) despite having the second lowest average (1.793) after Hungary (1.650). Similarly shows the lowest teacher behavior issues (1.644) followed by Poland despite the latter having the highest maximum value in this variable across all countries (4.0). Moreover, for resources issues, Hungary stands at the top of the rank (2.177) followed by Slovakia (1.975), which also have the highest variation in this variable (0.710), then Czech Republic (1.956) and finally Poland (1.868). Additionally, for staff-related issues, Slovakia and Hungary exhibit relatively high means (1.875 and 1.917 respectively), which suggests that there might be concerns regarding the availability or quality of assisting staff or teaching conditions. However, the Czech Republic (1.885) and Poland (1.5) show lower average values in staff issues, hinting at possibly better staff conditions or fewer concerns in these aspects. Notably, Slovakia and Czech Republic both have the highest maximum value (3.75) for staff issues, indicating some schools might face more significant challenges in this area.Regarding competition (COMP), the Czech Republic and Poland present lower average values (1.617 and 1.312 respectively), suggesting less competition among schools, which could mean fewer options for parents and potentially larger catchment areas for each school, especially for Poland which exhibits the lowest variation among the four countries (0.636). Hungary (1.675) and Slovakia (1.549) on the other hand show slightly higher averages, indicating higher competition among schools within these countries. When looking at school size by number of students (SCSIZE), Poland and Hungary exhibit the largest average sizes (508.714 and 497.228 respectively) and the highest variations as well (297.766 and 271.114 respectively). Conversely, the Czech Republic and Slovakia have smaller average school sizes (459.782 and 389.675 respectively). In terms of the community type where schools are located (LOC), Poland has the highest urban representation in term of mean (0.808), suggesting a greater proportion of schools in urban areas. Hungary follows with a mean value of (0.714), indicating a substantial urban presence as well. The Czech Republic and Slovakia have lower mean values, (0.569 and 0.488 respectively), suggesting a higher proportion of schools in rural areas in these countries. Lastly, the total number of teachers (TOTAT) shows Poland with the highest average (48.912) and the highest variation as well (23.701). Hungary follows with an average of (45.182), while the Czech Republic (36.267) and Slovakia (31.006) have lower averages, possibly indicating fewer resources in terms of teaching staff, which could impact the quality of education provided.

@@

However, an interesting debate has took place regarding the statistical plausibility of second stage regression. On the one hand, advocates of this approach argue that the simplicity and versatility of the approach allows for valuable and practical insight. OLS or Tobit regressions are usually used in this context allowing for inference, in fact [@hoff2007] provided a review of the use of tobit and OLS regression in a second stage, and advocated for the use of tobit. On the other hand opponents to the approach advocate for a more careful specifications, since a two-stage analysis doesn't stem for a data generating process (DGP), thus it's quite difficult to understand what is exactly being estimated in the second stage. One of the earliest critics of this approach was [@grosskopf1996] who specified that other than the lack of a DGP, there's a possibility that these non-discretionary variables of the second stage can be correlated with the output efficiency of the first stage. Both [@grosskopf1996] and [@ramalho2010] argued against the use of linear models in the second stage. Building on this criticism, [@simar2007] was the first paper that coherently justified the use of a two-stage DEA proposing a DGP and two bootstrap algorithm that enable inference in the second stage with a truncated regression. The basic idea behind [@simar2007] work, is that DEA efficiency scores are non-parametrically estimated, thus they are a non-observed estimate of an unkown efficiency frontier which means that these scores do not account for stochasticity (i.e: any deviation from the efficiency frontier is entirely due to inefficiency) which means that using non-parametric methods in the second stage is more appropriate as proven and discussed in [@simar2011], hence the bootstrap algorithms.

@@

The results of the first stage DEA estimation (table 4) indicate that Poland is the most efficient country according to our specifications (1.183), followed by Slovakia (1.226). Then Hungary with a score of (1.253) who exhibits the largest variation in efficiency (0.172), while the Czech Republic ranks as the least efficient country (1.269).

```{r tab4, echo=FALSE}
dea_out_1 %>%
  mutate(efficiency_scores = map(dea_out, ~.$eff)) %>%
  summarise(
    mean_efficiency = mean(unlist(efficiency_scores)),
    sd_efficiency = sd(unlist(efficiency_scores)),
    min_efficiency = min(unlist(efficiency_scores)),
    max_efficiency = max(unlist(efficiency_scores))
  ) %>% 
  arrange(mean_efficiency) %>% 
  gt(rowname_col = 'CNT') %>% 
  fmt_number(
    columns = 2:last_col(),
    decimals = 3
  ) %>% 
  tab_footnote(footnote = 'Efficient units are has value closer to 1') %>% 
  tab_header(
    title = 'Table 4: Average efficiencies for each country'
  )
```

In the table 5 and figure 1, we can see the distribution of schools across the efficiency quartiles. Poland present the biggest number of fully efficient schools (efficiency score = 1) with (5.46%) of the total number of schools, followed by Hungary (3.54%), Slovakia (3.32%), and lastly Czech Republic (1.92%). However, when we check the forth quartile of efficiency for each country we observe that Poland also has the most percentage of highly inefficient schools (24.79%) followed with close percentage by Czech Republic (23.98%). Additionally, in table 7, we calculated the frequency for null and non-null multiplier wights. These wights depict the importance that each DMU (school) give to each output when the efficiency score is being calculated for it. We can observe that science subjects have the most influence Polish and Czech schools' efficiency (55.56% and 48.62% respectively of schools have non-null weights) whereas mathematics is the influencing subject for Hungarian schools (39.81%) and Slovakian schools as well (73.98% highest among all countries)

```{r tab5, echo=FALSE, warning=FALSE}
# Extract efficiency scores, compute quartiles, and mark fully efficient schools.
dea_by_quartile <- dea_out_1 %>% 
  mutate(
    eff_scores =  map(dea_out, ~pluck(.x, "eff"))
  ) %>% 
  unnest(eff_scores) %>% 
  mutate(
    full_eff = if_else(eff_scores == 1, 1, 0),
    quartiles = cut(eff_scores,
                    breaks = quantile(eff_scores, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = TRUE),
                    labels = c('Q1', 'Q2', 'Q3', 'Q4'),
                    include.lowest = TRUE)
  )
# Calculate and display count and percentage of schools in each quartile, including fully efficient ones.
dea_by_quartile %>% 
  mutate(
    quartiles_ineff = if_else(full_eff == 1, "FE", quartiles)
  ) %>% 
  count(quartiles_ineff) %>% 
  mutate(
    p = case_when(
      CNT == 'CZE' ~ (n / 399)*100,
      CNT == 'HUN' ~ (n / 206)*100,
      CNT == 'POL' ~ (n / 234)*100,
      CNT == 'SVK' ~ (n / 246)*100
    ),
    p = glue::glue('({round(p, 2)}%)')
  ) %>% 
  unite(p, c('n','p'), sep = '  ') %>% 
  pivot_wider(names_from = quartiles_ineff, values_from = p) %>% 
  ungroup() %>% 
  arrange(FE) %>% 
  gt(rowname_col = 'CNT') %>% 
  tab_header(
    title = 'Table 5: Distribution of Efficiency Scores by Country and Quartile'
  )
```

```{r tab6, echo=FALSE}
# Function to calculate the number of zero and non-zero values in each column
count_zeros_and_nonzeros <- function(matrix) {
  # Count non-zero values
  non_zero_counts <- colSums(matrix != 0)
  # Count zero values
  zero_counts <- colSums(matrix == 0)
  # Combine into a data frame for easier viewing
  # Count non-zero values
  non_zero_avg <- colMeans(matrix != 0)
  # Count zero values
  zero_avg <- colMeans(matrix == 0)
